Spike spectra for recurrences

### 2022-07-22 Manuscript/inter_spike_manuscript_mdpi.tex
comment no. 2
Last try for CENOGRID

% Authors, for the paper (add full first names)
\Author{K. Hauke Kraemer $^{1,}$*\orcidA{}, Frank Hellmann $^{1,}$, Mehrnaz Anvari $^{1,4}$, J\"urgen Kurths $^{1,2,4}$ and Norbert Marwan $^{1,3,}$*}

@@

\subsection{Period estimation for different dynamics in the R\"ossler system}
First, we consider the R\"ossler system (Eq.~\eqref{eq_model_roessler} in Appendix \ref{sec_models_roessler}) 
in three different dynamical setups. We use the proposed inter spike spectrum to
identify the type of dynamics.
We set the parameters $b=2$, $c=4$ and analyze period-2 limit cycle dynamics ($a=0.36$ in Fig.~\ref{fig_tau_rr_example_roessler}A, D, G, J), 
period-3 limit cycle dynamics ($a=0.41$ in Fig.~\ref{fig_tau_rr_example_roessler}B, E, H, K) and chaotic dynamics ($a=0.428$ in Fig.~\ref{fig_tau_rr_example_roessler}C, F, I, L).

@@

\subsection{Bifurcations in the Logistic map}

@@

\subsection{Inter spike spectra of power grid frequency data}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

>>>>

% Authors, for the paper (add full first names)
\Author{K. Hauke Kraemer $^{1,}$*\orcidA{}, Frank Hellmann $^{1,}$, Mehrnaz Anvari $^{1}$, J\"urgen Kurths $^{1,2,4}$ and Norbert Marwan $^{1,3,}$*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Period estimation for different dynamics in the R\"ossler system}
First, we consider the R\"ossler system (Eq.~\eqref{eq_model_roessler} in Appendix \ref{sec_models_roessler}) 
in three different dynamical setups. We use the proposed inter spike spectrum to
identify the type of dynamics.
We set the parameters $b=2$, $c=4$ and analyze period-2 limit cycle dynamics ($a=0.36$ in Fig.~\ref{fig_tau_rr_example_roessler}A, D, G, J), 
period-3 limit cycle dynamics ($a=0.41$ in Fig.~\ref{fig_tau_rr_example_roessler}B, E, H, K) and chaotic dynamics ($a=0.428$ in Fig.~\ref{fig_tau_rr_example_roessler}C, F, I, L).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Bifurcations in the Logistic map}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Inter spike spectra of power grid frequency data}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evolutionary inter spike spectra of astronomical data}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}\label{sec_tau_rr_discussion}
